Safe Transferable Regions

### 2015-11-13 paper/overview2.tex
updates to motivating example
updated overview

\begin{figure}
\begin{codejava}
  public class Region<T> {
    public Region(Func<void,T> mkRoot);
    public void free();
    public void transfer();
  }
\end{codejava}
\caption{The type signature of the \C{Region} class}
\label{fig:region-class}
\end{figure}

@@

The key to memory safety in \name is the following restriction:
an object $o_1$ in a region $R_1$ is allowed to store a pointer to
an object $o_2$ in a region $R_2$ only if $R_2$ is guaranteed to outlive $R_1$.
(A similar restriction applies in the case where $o_1$ is a stack-allocated variable.)

>>>>

\begin{figure}
\begin{codejava}
  public class Region<T> {
    public Region(Func<T> mkRoot);
    public void free();
    public void transfer();
  }
\end{codejava}
\caption{The type signature of the \C{Region} class}
\label{fig:region-class}
\end{figure}

@@

Our goal is a type system that can ensure the memory safety of programs that use the region
constructs described above.
The key to memory safety in \name is the following restriction:
an object $o_1$ in a region $R_1$ is allowed to store a pointer to
an object $o_2$ in a region $R_2$ only if $R_2$ is guaranteed to outlive $R_1$.
(A similar restriction applies in the case where $o_1$ is a stack-allocated variable.)
